\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-06 trunk/arch.tex
Update on the introduction of T-REX

The T-REX architecture was designed with the objective to bring 
planning closer to the low-level control of the vehicle while
maintaining its reactivity. Indeed, in most of the architecture where
task planning is embedded, this task remains at a failry high level of
abstraction as the complexity of this task would otherwise impede the
system reactiveness. As a result the planning problem managed {\em in
  situ} remains fairly detached from low-level control and most of the 
reactive adaptation which in contrast is managed by specialized 
component that relies on different representations for modeling 
the local behavior they control or even do not have any explicit 
formal model of this behavior. Taking cues from the IDEA 
architecture \cite{mus02}, we designed a core framework that provides a
formal basis \cite{Py:2010ti} on the way each of the sub-component --
called reactors -- of our agent can interact by exchanging only
information through {\em state variables} by ensuring that state 
information can propagate through all the reactors ensuring a
consistent view of the present state of the world at every single tick
trough a bottom-up {\em synchronization} flow and collaboration for
future state evolution by timely exchanges of goals on {\em state
  variables}. This exchange does not impose to any reactor to be aware
of the reactors it is connected to but only focus on the state
variables it relies on (called {\em external}) and the state
variables it manages and maintains (called {\em internal}).

>>>>

The T-REX architecture was designed with the objective to bring 
planning closer to the low-level control of the vehicle while
maintaining its reactivity. Indeed, in most of the architecture where
task planning is embedded, this task remains at a failry high level of
abstraction as the complexity of this task would otherwise impede the
system reactiveness. As a result the planning problem managed {\em in
  situ} remains fairly detached from low-level control and most of the 
reactive adaptation which in contrast is managed by specialized 
component that relies on different representations for modeling 
the local behavior they control or even do not have any explicit 
formal model of this behavior. The two angles our architecture attck
this issue are the following:
\begin{itemize}
\item Distribute the global planning problem into multiple decision
  loops, called {\em reactors}. Each reactor have its own scope both 
  functionally (one for example focusing on the conversion of high 
  level waypoints into low-level commands) and temporally as 
  each reactor specifies to the agent their planning look-ahead and
  their expected latency before being able to produce plan.
\item Enforce a stronger interaction between the planning process 
  and the integration of the world evolution. The objective being to
  make sure that the plannign task is done while continuously informed 
  on new world state change. By doing so, we expect to allow the planner
  tohave better informed decision despite the fact that its latency is
  larger that the world change rate.
\end{itemize}

For the first point T-REX provides a formal framework described in
details in \cite{Py:2010ti} and is not the focus of this paper. The
second have deep implication on how on should integrate a planner in
this framework in general and was applied to the europa framework
specifically. We'll develop later how this requirement implies to see
in-situ planning as two parallels processes that are tightly linked
through the same plan structure. But before that we need to introduce
at least the high leve lconcepts and ideas behind our architecture as
a whole.

T-REX architecture is structured around the notion of 
{\em state variables} as the unique basis of interactionalong
with a well defined ownership  model for each of these. 
In this framework each reactor is seen as a
black box providing its own {\em internal} state variables for which
its is reponsible to maintain its value at every single instant --
represented by a {\em tick} with a fixed duration. In order to
identify its state a reactor can subscribe to {\em external} state
variables for  which it will received new updates when the owner of
these will produce its {\em internal} state. This {\em
  synchronization} process progate through the reactor dependency 
graph on a bottom up flow at every {\em tick} ensuring that all the
reactors have a consistent view of the world. Conversely each reactor
can request a future change on one of its {\em external} state
varaiable which will be transfromed as an {\em internal} goal to the
owner. This goal is expected to porduce a deliberation phase on the
receiver which can in turn produce a plan impacting its {\em external}
state variables that will propagate down following the same
mechanism.

% Taking cues from the IDEA 
% architecture \cite{mus02}, we designed a core framework that provides a
% formal basis \cite{Py:2010ti} on the way each of the sub-component --
% called reactors -- of our agent can interact by exchanging only
% information through {\em state variables} by ensuring that state 
% information can propagate through all the reactors ensuring a
% consistent view of the present state of the world at every single tick
% trough a bottom-up {\em synchronization} flow and collaboration for
% future state evolution by timely exchanges of goals on {\em state
%   variables}. This exchange does not impose to any reactor to be aware
% of the reactors it is connected to but only focus on the state
% variables it relies on (called {\em external}) and the state
% variables it manages and maintains (called {\em internal}).
